A finite-state morphological transducer for Kyrgyz

### 2012-03-15 paper/paper.tex
colon
more

We have evaluated the analyser in two ways. The first is by calculating the naïve coverage and mean ambiguity 
on two large freely available corpora of Kyrgyz. The second is by performing an evaluation of precision and recall on a smaller, hand-validated test set.

@@

The results for precision and recall are presented in Table~\ref{table:precrecall}. That the precision is so high is not surprising, the transducer is rule-based and the test set is the corrected output of the analyser. In order to get a more accurate figure for precision, it would be necessary to have several linguists review the set. Low recall is due to forms which do not receive any analyses, in all cases this was due to missing stems in the lexicon. Out of the 1,000 words, 91 did not receive any analyses. Of these, 52 forms were proper names 28 were nouns, 6 were adjectives and the remaining 5 verbs. 
This would suggest that in terms of adding new stems, it would be a good idea to look at increasing both the number of proper names, and nouns.

>>>>

We have evaluated the analyser in two ways. The first is by calculating the naïve coverage and mean ambiguity 
on two large freely available corpora of Kyrgyz. The second is by performing an evaluation of precision and recall on a smaller, hand-validated test set. The revision of the transducer evaluated was \texttt{{\small r36739}}.

@@

The results for precision and recall are presented in Table~\ref{table:precrecall}. That the precision is so high is not surprising: the transducer is rule-based and the test set is the corrected output of the analyser. In order to get a more accurate figure for precision, it would be necessary to have several linguists review the set. Low recall is due to forms which do not receive any analyses, in all cases this was due to missing stems in the lexicon. Out of the 1,000 words, 91 did not receive any analyses. Of these, 52 forms were proper names 28 were nouns, 6 were adjectives and the remaining 5 verbs. 
This would suggest that in terms of adding new stems, it would be a good idea to look at increasing both the number of proper names, and nouns.
